**R Markdown Presentation & Plotly : Developing Data Products Week 3 Assignment**
#Bharath Kumar R
#08-01-2020

**Instructions**

1.Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly.

2.Review criteria : The rubric contains the following two questions:

+ Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

+ Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

**Crude Oil Price Data**

*Time series of major Crude oil Prices explanis about the increase in the oil price.*

1.Dataset contains daily and Monthly prices of crude oil starting from 26-12-2014  to 26-12-2019. Prices are in nominal dollars per barrel.


# License : Public domain data is availabe in FRED ECONOMIC RESEARCH

## Link: https://fred.stlouisfed.org/categories/32455


```{r}
sourceData <- read.csv("oil_price.csv", stringsAsFactors = FALSE)
head(sourceData)
```

```{r}
## Assigning titles to X & Y axis.
x <- list(title = "Years")
y <- list(title = "Price in USD")

```

**Plot of Natural Gas Prices using Plotly**
```{r}

plot_ly(sourceData, x = ~as.Date(DATE), y = ~price.in.USD, type = 'scatter')
```



